Finite-state morphological transducers for three Kypchak languages

### 2014-02-16 kipchak-lrec-2013/kipchak-paper.tex
submitted version
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48181 72bbbca6-d526-0410-a7d9-f06f51895060
sadly, I'm not a t IMS yet
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@50131 72bbbca6-d526-0410-a7d9-f06f51895060
numbers
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@50288 72bbbca6-d526-0410-a7d9-f06f51895060

\author{Jonathan North Washington \\
Departments of Linguistics and Central Eurasian Studies\\
Indiana University\\
Bloomington, IN 47405 (USA)\\
\texttt{jonwashi@indiana.edu} \and
Ilnar Salimzyanov  \\
Institut für Maschinelle Sprachverarbeitung \\
Universität Stuttgart\\
Stuttgart (Germany) \\
\texttt{ilnar@ilnar} \and 
Francis M. Tyers\\
Departament de Llenguatges i Sistemes Informàtics \\  
Universitat d'Alacant\\
E-03071 Alacant (Spain)\\
\texttt{ftyers@dlsi.ua.es} 
}

@@

%The corpora were obtained from:
% Wikipedia:
% RFE/RL
% Yoldaš: 
% New testaments:

% kaz: 
% tat:

@@

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\midrule
\multirow{4}{*}{Kazakh} & Wikipedia 2013 &  -  &  - \\
	& RFE/RL 2010 & 3.2M & - \\
	& Bible & 577K & - \\\cline{2-4}
	& Average & - & 90.5\% \\
\midrule
\multirow{4}{*}{Tatar} & Wikipedia 2013 & 128K &  - \\
	%FIXME: the News corpus isn't RFERL, pretty sure; maybe we should test just on RFERL content?
	& News 2005--2011 & 4.6M & - \\
	& New Testament & 137K & - \\\cline{2-4}
	& Average & - & 89.0\% \\
\midrule
\multirow{3}{*}{Kumyk} & Yoldaš & 287K &  - \\
	& New Testament & 154K & - \\\cline{2-4}
	& Average & - & 90.1\% \\
\bottomrule
\end{tabular}
 \caption{Corpora used for naïve coverage tests}
 \label{table:corpora}
\end{center}
\end{table}

>>>>

\author{Jonathan North Washington \\
Departments of Linguistics and Central Eurasian Studies\\
Indiana University\\
Bloomington, IN 47405 (USA)\\
\texttt{jonwashi@indiana.edu} \and
Ilnar Salimzyanov  \\
Kazan Federal University \\
Kazan, Republic of Tatarstan\\
(Russian Federation) \\
\texttt{ilnar.salimzyan@gmail.com} \and 
Francis M. Tyers\\
Departament de Llenguatges i Sistemes Informàtics \\  
Universitat d'Alacant\\
E-03071 Alacant (Spain)\\
\texttt{ftyers@dlsi.ua.es} 
}

@@

% Tatar, religion: tat.nt.ibt.txt, tat.quran.nughmani.txt.bz2
% Tatar, wp: tat.wikipedia.2013-02-25.txt.bz2
% Tatar, news: tat.news.2005-2011_300K-sentences.txt.bz2
% Kazakh, religion: kaz.bible.kkitap.txt.bz2, kaz.quran.altay.txt.bz2
% Kazakh, wp: kaz.wikipedia2.2013.txt.bz2
% Kazakh, news: kaz.rferl.2010.xml.bz2, kaz.rferl2.2012.txt
% Kumyk, religion: kum.nt.ibt.txt, (kum.genesis.ibt.txt)
% Kumyk, news: kum.yoldash.2013.txt, kum.articles.kumukia.txt.bz2

@@

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} (\%) \\
\midrule
\multirow{4}{*}{Kazakh} & Wikipedia &  -  &  - \\
	& News & 3.2M & - \\
	& Religion & 577K & - \\\cline{2-4}
	& Average & - & 90.5\% \\
\midrule
\multirow{4}{*}{Tatar} & Wikipedia & 128K &  - \\
	%FIXME: the News corpus isn't RFERL, pretty sure; maybe we should test just on RFERL content?
	& News & 4.6M & - \\
	& Religion & 137K & - \\\cline{2-4}
	& Average & - & 89.0\% \\
\midrule
% news = kum.yoldash.2013.txt
% religion = kum.genesis.ibt.txt, kum.nt.ibt.txt
\multirow{4}{*}{Kumyk} & Wikipedia & -- & -- \\
        & News & 287K &  91.4 $\pm$ 0.7 \\
	& Religion & 227K & 92.0 $\pm$ 1.1 \\\cline{2-4}
	& Average & - & 91.7 $\pm$ 0.7 \\
\bottomrule
\end{tabular}
 \caption{Corpora used for naïve coverage tests}
 \label{table:corpora}
\end{center}
\end{table}
